Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-03-10 strang/paper.tex
Add Garcia-Senz
Reword

There are several different approximations that people make in the
literature to this operator-split reacting system, in order to make
integrating the reaction system computationally less expensive:
\begin{itemize}
\item Evolve $(X_k)$ only.  This neglects temperature evolution
  completely in the burn, only evolving Eq.~\ref{eq:species}.  This is
  the method used in \citet{flash}. \MarginPar{other codes?}

\item Evolve $(X_k, T)$.   This is used in \cite{Pakmor:2012}.  To avoid
  expensive equation of state calls
  in getting the specific heat, we can optionally ``freeze'' the value
  of $c_v$ at the start of integration to avoid potentially expensive
  equation of state calls.  This was discussed in \cite{Bell:2004} and
  until recently was the default method in \castro.

>>>>

There are several different approaches taken in the literature to
this operator-split reacting system, including some approximations
that make integrating the reaction system computationally less expensive:
\begin{itemize}
\item Evolve $(X_k)$ only.  This neglects temperature evolution
  completely in the burn, only evolving Eq.~\ref{eq:species}.  This is
  the method used in \citet{flash}. \MarginPar{other codes?}

\item Evolve $(X_k, T)$.   This is used in \cite{Pakmor:2012} and
  \cite{Garcia-Senz:2013}.  To avoid expensive equation of state calls
  in getting the specific heat, we can optionally ``freeze'' the value
  of $c_v$ at the start of integration to avoid potentially expensive
  equation of state calls.  This was discussed in \cite{Bell:2004} and
  until recently was the default method in \castro.
